% assign each to a bank, give interest.
% write out descriptions (with highlighted clues.)
% add in inventories
% make cash flows all net to magic number at end of period.
% fix circular reference caused by cash asset (by using magic number!)
% hide letters:
% in income before taxes line
% in net cash flows from opex line
% in total current assets line
% in stockholders' equity (assets - liabilities)

\documentclass[10pt]{article}
\small

\usepackage{color}
\usepackage{latexsym,amssymb}
\usepackage{relsize,fancyhdr,multicol,array,multirow,amsmath}
\usepackage{tikz}
\usepackage{wordlike}
\usepackage{etoolbox}
\usepackage{siunitx} % allows aligning a tabular to a decimal point.

%\usepackage{forloop}

\usepackage{colortbl}

% create a column type to align at the decimal point.
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{.}{-1}}

% end usepackage statements

%\addtolength{\oddsidemargin}{-.875in}
%\addtolength{\evensidemargin}{-.875in}
%\addtolength{\textwidth}{1.75in}

\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}
\addtolength{\leftmargin}{-.5in}
\addtolength{\textwidth}{.5in}

\setlength{\parskip}{10pt plus 1pt minus 1pt}
\setlength{\parindent}{0pt}

% now some logic

\newtoggle{solution}
\toggletrue{solution}
\togglefalse{solution}

% set the colors for solution / puzzle:

\iftoggle{solution}{
\definecolor{soln-black}{gray}{0.0}
\definecolor{soln-lightblue}{rgb}{0.4,0.5,1}
}
{
\definecolor{soln-black}{gray}{1.0}
\definecolor{soln-lightblue}{rgb}{1,1,1}
}

% set definition that depend on colors:

\newcommand\mybox[2][]{\tikz[overlay]\node[fill=soln-lightblue!20,inner sep=2pt, anchor=text, rectangle, rounded corners=1mm,#1] {#2};\phantom{#2}}

% and now the document

\begin{document}

\iftoggle{solution}{

\setcounter{page}{0}

\section*{Growth and Fixed Costs: \textcolor{soln-lightblue}{Solution}}

\input{flavortext}
{\fontfamily{cmr}\selectfont
Things to notice about the financial statements:

\vspace{-.1in}
\begin{itemize}

\item There is enough information to match the company profiles to the
  financial statements, and so put the financial statements in order.

\item The number ``614050'' appears frequently and is in a different font.  This should be the most notable thing about the cash flow statements.

\item When the statements are put in order, the tax amounts (in the statement of operations) can be converted to numbers to read ``Taxes form a red herring.''

\item some lines in the Statement of Assets \& Liabilities don't add
  up right: they're off by a number between 1 and 26.

\end{itemize}
\vspace{-.1in}

Given the above, the steps to solving this puzzle are:

\vspace{.1in}
\textbf{\large 1. Match statements to company descriptions}

This gives an ordering of the financial statements.  

The keys to matching are:

\vspace{-.1in}
\begin{itemize}

\item Size of a company: there are a few initial revenue numbers: 100,000; 50,000; 30,000; 10,000.

\item Speed a company gets paid or pays its bills: 
``Receivables days'' and ``payables days'' are well-defined concepts.

\item Amount of inventory a company holds:\\
Restaurants, for instance, hold inventory only for a few days because most of it is perishable.

Note that the puzzle should be solvable without knowing those things
in advance, since ``payables days'', ``receivables days'', and
``inventory days'' are referred to in a company description, and these
are google-able.

\item interest paid on loans: higher by customers of First Wonderland, lower by customers of the Standard Bank.

\item ``Intangible assets'' or brand worth, held by companies with consumer brands

\item ``Goodwill'' some companies have accumulated by acquiring companies for more than the acquisitions' book values

\item And a few special items, such as:

\begin{itemize}
\vspace{-.1in}
\item legal fees awarded from one company to another

\item dividends paid by companies owned by the Red Queen or White King

\end{itemize}

\end{itemize}
\vspace{-.1in}

\vspace{.1in}
\textbf{\large 2. Find errors in the financial statements; convert to letters}

These are lines that don't ``add up''.  Each statement has a line off
by a value $<$ 26; these can be converted to letters (1 = A, 2 = B, etc) to
spell the clue phrase ``SEARCHHBSPHARVARDEDU'' or Search
hbsp.harvard.edu .

\vspace{.1in}
\textbf{\large 3. Search for the out-of-place number}

If you search hbsp.harvard.edu for ``13024''--- every company's
cash balance at the end of the period, the only number introduced
that's not a multiple of 100, and the amount of other items such as
legal fees or goodwill---you get a case with subtitle ``Women are the
solution'' (for testsolving) or with title ``The answer is secondary''
during hunt.

}}{}

\newpage


\iftoggle{solution}{
\section*{Growth and Fixed Costs: \textcolor{soln-lightblue}{Solution}}
}{
\section*{Growth and Fixed Costs}
}

\input{flavortext}

%\input{descriptions}

\foreach \n in {1,...,20}{
      \input{tabular-open}
      \textbf{{\n}. \input{\n}}\\
      \input{desc-\n}\\
      \input{tabular-close}
}


% \iftoggle{solution}{
%     \foreach \n in {1,...,20}{
%       \begin{tabular}{p{0.4\textwidth} | c  | c  | c  | c  | c  | c  | c  | c  | c  | c | c  | c  | c  |}
%       \textbf{{\n}.} \input{\n} & \hspace{10pt}  & \hspace{10pt}  & \hspace{10pt}  & \hspace{10pt}  & \hspace{10pt}  & \hspace{10pt}  & \hspace{10pt}  & \hspace{10pt}  & \hspace{10pt}  & \hspace{10pt}  & \hspace{10pt} & \hspace{10pt} & \hspace{10pt}\\
%       \hline
%       \end{tabular}\\
%     } % close foreach    
% }{}

\foreach \n in {12,19,3,6,16,8,11,18,9,2,17,7,1,13,20,5,15,4,10,14}{
%\foreach \n in {1,...,20}{
    \newpage

    \iftoggle{solution}{
      \input{tabular-open}
      \textbf{{\n}. \input{\n}}\\
      \input{desc-\n}
      \input{tabular-close}
    }{
      \vspace{2in}
    }
    \input{statement-\n}

    \input{soln-\n}


  }%


\end{document}
